\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-02-27 archive.tex
added a bunch of logo figures

Our work sits within the Exploration-Compression (EC) family of
algorithms.  EC~\cite{Dechter:2013:BLV:2540128.2540316} is a program
induction framework where an agent alternates between searching, or
`exploring', the space of programs, and then updating its search
procedure by compressing programs found during exploration. \system
grew directly out of research on EC-style systems and both of our
sleep phases can be interpreted as a kind of compression:
consolidation aims to compactly refactor code, while the recognition
model aims to encode a program in as few bits as possible, conditioned
on a task. Other offshoots of EC include our previous work,
EC$^2$~\cite{ecc}, the direct predecessor of \systemEnding; and the
neurosymbolic framework in~\cite{lazaro2019beyond}. Closely aligned ideas
go much further back~\cite{solomonoff1989system,schmidhuber2004optimal}.

>>>>

Our work sits within the Exploration-Compression (EC) family of
algorithms.  EC~\cite{Dechter:2013:BLV:2540128.2540316} is a program
induction framework where an agent alternates between searching, or
`exploring', the space of programs, and then updating its search
procedure by compressing programs found during exploration. \system
grew directly out of research on EC-style systems and both of our
sleep phases can be interpreted as a kind of compression:
consolidation aims to compactly refactor code, while the recognition
model aims to encode a program in as few bits as possible, conditioned
on a task. Our previous work, EC$^2$~\cite{ecc}, introduced
neurally-guided search into the EC framework and served as the
starting point for \systemEnding.  Our work here extends EC$^2$ by (1)
introducing a new refactoring compression algorithm, (2) enriching the
neural network with a new bigram-over-trees parameterization and loss
function that together learn to break symmetries, accelerating program
search during waking, and (3) demonstrating how this family of
approaches can be applied to planning and generative modeling
problems.  Other offshoots of EC include the neurosymbolic framework
in~\cite{lazaro2019beyond} and the hierarchical Bayesian program
learner in~\cite{DBLP:conf/icml/LiangJK10}. Closely aligned ideas go
even further back~\cite{solomonoff1989system,schmidhuber2004optimal}.
